---
title: "RGL and Rmarkdown"
subtitle: "Interactive 3D plotting"
author: Ott Toomet
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: 
  html_document:
    highlight: tango
    df_print: kable
    fig_caption: false
toc: true
urlcolor: blue
---

# Introduction

This demo introduces using _rgl_ library with knitr.  _rgl_ contains
various openGL-based interactive 3d graphics display routines.  It's
installation may be a bit tough, on compiled systems you need to
install a number of graphics-related libraries, and the recent
incarnations of it also need _pantomjs_, a javascript library.
Installation of the latter is possible from within R though.  Needless
to say, your graphics card driver must support 3d acceleration.

3D is also more memory, cpu, and graphics card intensive.  While
simple animations should work smoothly on all laptops (I have done
some with Pentium 3 PC of early 2000-s), many smooth surfaces and
visual effects require a fast graphics card.

```{r setup}
library(rgl)
rgl::setupKnitr()
                           # let rgl and knitr talk together
```


# Some example functions

3D scatterplot with spheres

```{r}
with(iris,
                           # 'iris' is a standard dataset
     plot3d(Sepal.Length, Sepal.Width, Petal.Length,
                           # dimensions petals
            type="s",
                           # spheres
            col=1 + as.numeric(Species),
                           # color according to species
            alpha=0.5
                           # 50% transparent spheres
            )
     )
rglwidget()
                           # Output the webGL widget
```

Try to rotate (with mouse), zoom (with mouse scrolling)


# 3D surface of parabola

3D image of the same parabola we used for `contour`.

```{r}
f <- function(x, y) x^2 + 2*x*y + 3*y^2
x <- seq(-4, 4, length.out=100)
y <- seq(-4, 4, length.out=100)
z <- outer(x, y, f)
persp3d(x, y, z, color="green")
rglwidget(elementId="surface")
```


# 3D iso-surface plot example

3d countour plot (analogous to 2d `countour`) is living in _misc3d_
package.

Note: the calculations take a bit of time, and the resulting html file
is huge.

If you wish, you can experiment with larger grid size but that
requires fast CPU and fast graphics.  But it should be no issue with
powerful modern gaming computers!

```{r}
A <- matrix(1:9, 3, 3) + 2*diag(3)
A
quadForm <- function(x, y, z)
   t(c(x,y,z)) %*% A %*% c(x,y,z)
                           # compute an elongated 3d parabola 
levels <- c(10, 60, 140)
                           # draw the surfaces where the parabola has these
                           # values
nGrid <- 20
                           # Grid size.  If you have powerful gaming pc,
                           # increase these to 100 to get smoother image
aspect3d("iso")
misc3d::contour3d(function(x, y, z) {
           mapply(quadForm, x, y, z) },
                           # compute the function values on 3d grid
           ## if you wish, run the computations in parallel:
           ## replace the mapply above with:
           ## parallel::mcmapply(quadForm, x, y, z,
           ##                    mc.cores=parallel::detectCores()/2) } ,
           level=levels,
           x = seq(-4, 4, length=nGrid),
           y = seq(-4, 4, length=nGrid),
           z = seq(-4, 4, length=nGrid),
           color = RColorBrewer::brewer.pal(length(levels), "Set3"),
           alpha=0.5
           )
rglwidget(elementId="3dcontour")
```
