---
title: "RGL and Rmarkdown"
subtitle: "Interactive 3D plotting"
author: Ott Toomet
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: 
  html_document:
    highlight: tango
    df_print: kable
    fig_caption: false
toc: true
urlcolor: blue
---
# Introduction


## Random normals

Create 1000 random normal numbers.  Create it in a code block and show
the code.  Display a full sentence where you tell what is the mean of
these numbers.

```{r echo=TRUE}
x <- rnorm(1000)
```
the mean is `r mean(x)`



## Histogram

Create a histogram of the normals above.  Use good descriptive
labels.  Do _not_ show your code!
```{r echo=FALSE}
hist(x)
```

## Random uniform numbers

Create a large number of random uniform numbers.  Create a histogram
of the result.  You may want to play with `breaks` option of the
`hist` function.  Make your figure large: explore `fig.width` and
`fig.height` chunk options.


## Scatterplot

Create a scatterplot of a large number of random normals, i.e. pick
random normal $x$, random normal $y$, and plot x versus y.


## Fix the YAML header

Fix the YAML header of this file.  Give it a descriptive title,
correct author name, and change some of the formating options.


## Throw a die

Throw a die 10 times.  Report inline how many 6-s you got.

Note: you may want to use `sample` function to simulate die rolls.



## Fueleconomy by number of cylinders

Take the fueleconomy::vehicles data.  Compute the mean fuel economy by
grouping the vehicles by number of cylinders.  Plot this as a
barplot.  Ensure you label your bars!

