---
title: "RGL and Rmarkdown"
subtitle: "Interactive 3D plotting"
author: Ott Toomet
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: 
  html_document:
    highlight: tango
    df_print: kable
    fig_caption: false
toc: true
urlcolor: blue
---
# Introduction


## Random normals

> Create 1000 random normal numbers.  Create it in a code block and show
> the code.  Display a full sentence where you tell what is the mean of
> these numbers.

```{r}
x <- rnorm(1000)
```
The mean of these numbers is `r mean(x)`.

## Histogram

> Create a histogram of the normals above.  Use good descriptive
> labels.  Do _not_ show your code!

```{r, echo=FALSE}
hist(x,
     xlab="random value", ylab="count", main=paste(length(x), "random normals"))
```


## Random uniform numbers

> Create a large number of random uniform numbers.  Create a histogram
> of the result.  You may want to play with `breaks` option of the
> `hist` function.  Make your figure large: explore `fig.width` and
> `fig.height` chunk options.

```{r fig.width=15, fig.heigth=12}
y <- runif(10000)
hist(y, breaks=100,
     xlab="random value", ylab="count", main=paste(length(y), "random uniforms"))
```


## Scatterplot

> Create a scatterplot of a large number of random normals, i.e. pick
> random normal $x$, random normal $y$, and plot x versus y.

```{r}
n <- 1e4
x <- rnorm(n)
y <- rnorm(n)
plot(x, y, main="random normals")
```


## Fix the YAML header

> Fix the YAML header of this file.  Give it a descriptive title,
> correct author name, and change some of the formating options.


## Throw a die

> Throw a die 10 times.  Report inline how many 6-s you got.
> 
> Note: you may want to use `sample` function to simulate die rolls.

```{r}
r <- sample(6, 10, replace=TRUE)
```

I got `r sum(r == 6)` sixes.



## Fueleconomy by number of cylinders

Take the fueleconomy::vehicles data.  Compute the mean fuel economy by
grouping the vehicles by number of cylinders.  Plot this as a
barplot.  Ensure you label your bars!

